Clouds and Radiation in a mock-Walker Circulation

### 2019-11-05 Silvers_WalkerCell.tex
several textual edits related to domain size dependence

%\textbf{Key Points: choose three}
\begin{keypoints}
  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
  maximum.}
  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
  maximum away from the SST maximum.}
  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
  changes in the low-level clouds and boundary layer structure.}
  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
  region that is 30\% higher than for the coarser cases with parameterized convection.}
  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
\end{keypoints}

@@

% What are climate modelers doing to reduce uncertainties about cloud processes?
The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  To elucidate this 
coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an idealized equatorial tropical Pacific.   In 
the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective storms.   In contrast, 
the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, non-precipitating clouds with a dry 
atmosphere above the clouds.  These regions are connected by a large-scale circulation.  We analyze this scenario in a high-resolution 
and coarse resolution simulation and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the Earth's sensitivity to 
changes in greenhouse gas concentrations.

A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
resolution (25km, 100km) configured 
as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
dramatically decreasing the grid-spacing we resolve much more of the dynamical motion and eliminate some of the statistical 
approximations of clouds, and thus more explicitly simulate some of their impacts.

@@

  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus/congestus, and congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been extensively studies (review paper?).  The circulation first 
  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep convection to the 
  eastern Pacific region which tends to be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  This circulation
   has come to be 
  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations (Walker, Bjerknes), theory (Geisler, 1981), 
  or modeling studies (Bretherton et al., 2006; Wofsy and Kuang, 2012).  The modeling studies have compared theoretical models with cloud
  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker Circulation with 
  simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
The reality is that we 
  were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  

@@

We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
highlight both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
we test the impact of convective parameterization, 
longwave radiation interactions with clouds, domain size, 
and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain size and resolution
because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.

The results of our experiments are organized as follows.  First, the general structure and characteristics of the steady state solutions
will be described.   Then, the influence of parameterized convection and the longwave cloud radiative effect on the overturning 
circulation will be shown.  We will then briefly discuss how the circulation changes as a function of domain size.  The last part of the
results will describe and contrast the Walker circulation in a GCM-like configuration and a CRM-like configuration as the 
resolution changes.

@@

\begin{table}
\begin{center}
\caption{Specifications of the simulations used most heavily in this study.  In the Convection
column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.}
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
    \\
 Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection     \\ \hline
  P100L &  100          &   800 $\times$ 16000    &  60              & prm                   \\ 
    \\
  P100 &  100                & 800 $\times$ 4000     & 60            & prm                     \\  
    \\
  P25L &  25             & 200 $\times$ 16000      & 60             & prm                     \\  
    \\
  P25  &  25             & 200 $\times$ 4000      & 60             & prm                   \\  
    \\
 E25  &   25          & 200 $\times$ 4000      & 60             & expl                \\  
    \\
 E2   &   2          & 100 $\times$ 4000      & 6             & expl                   \\ 
    \\
 E1   &   1          & 10 $\times$ 4000      & 6             & expl                 \\  \hline

@@

"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
greater are being dominated by this second factor.

@@

When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are 
two of the most fundamental choices that must be made.   One the goals of this study was to explore the results of 
changing grid-spacing over a wide range of values.  To simplify the analysis we have in most cases chosen to keep the 
long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
\cite{Bretherton2005, Bretherton2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
(e.g. Bretherton et al., 2005; Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013; 
Silvers et al., 2016; Patrizio and Randall, 2019) have 
documented sensitivities of the equilibrated state to domain size.   
The analysis of the previous, and of the next sections focus on results from 
experiments using a domain with a long domain length of $4000 \, \rm{km}$.  However we do find interesting 
sensitivities to the domain size that are noted here.

The evolution in time of the precipitation field reveals important characteristics of these simulations, and 
illustrates how much the distribution can vary as a function of domain size, parameterization of convection, 
and the effect of the longwave radiation due to clouds. 
Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovmoller plots of precipitation after 
averaging along the short horizontal dimension.  The four panels show simulations with a grid-
spacing of $25\, \rm{km}$ on a domain with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ 
(middle right), and 
simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
$16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LW CRE off.    
 At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
strengthen an overturning circulation and
narrow the region of deep convection (see Popp and Silvers, 2017, HH, Dixit et al. 2019.  etc.).
The structure of the precipitation changes more as a function of domain size than it does as a function of resolution. 
On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation which meanders within 
500 km of the SST maximum at the center of the domain,  
the experiments without the LW CRE basically have no region with consistently strong precipitation.  Instead, 
smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously notes, these
GCM-like simulations equilibrate after approximately 50 days.  However, there is also a dramatic change in 
the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
precipitation does not significantly change in these cases, only the spatial structure.

% new Hovmoller diagram
\begin{figure}
  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
  \caption{Evolution of precipitation through 3 years of simulation.  From left, large domain 100km, (P100L); 
  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
  For each resolution, the only difference between the two experiments shown is a domain length of 
  16,000 km or 4,000 km.}
  \label{fig:domdep}
\end{figure}

@@

Smaller domains were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
They also found less low-level clouds over the colder SSTs in the small domains, relative to a control domain size that was 4x
larger.   In contrast, here larger domains have larger precipitation rates (Table 2).  For the LWCRE off cases, in agreement 
with \citeA{Bretherton2006} we find a more 
focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the ascent region changes little between P25 
and P25L but for P100 and P100L the ascent region is much more focuses on the large domain.    
How do our low-level clouds over the colder SSTs compare with the findings of B06 (check the condensate for small vs. large 
domains)?

@@

The domain mean total precipitation is constrained by the radiative cooling of the atmosphere.  However, in 
models with the convection parameterized the 
total precipitation is composed of precipitation from the convection scheme and the large-scale cloud scheme. 
While the relative contribution of each component is not well constrained, it is thought to influence the 
atmospheric state (Held et al., what part of the state?). 
The distribution of convective and large-scale precipitation indicates how the condensational heating
in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
Precipitation from each of these two components is
shown in Figure \ref{fig:conv_vs_ls} as a function of both resolution and domain size.  
In the regions of large-scale ascent, most of the 
precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE (thick lines) dramatically increases
the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective precipitation 
but does act to spatially concentrate it.  With the exception 
of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in P25L case
and an almost complete elimination of the large-scale precipitation in the P100L case.

@@

@@

References:

Bretherton et al. 2006
Jeevanjee et al. 2018
Kuang and Wofsy
Muller and Held, 2012
Popp and Silvers, 2017
Patrizio and Randall, 2019
Randall et al., 1989
Silvers et al. 2016
Slingo and Slingo, 1988
Stevens et al. 2012
Zhao et al. 2018a
Zhao et al. 2018b

@@

%\bibliography{references}
%\begin{thebibliography}{}
%
%\bibitem[{\textit{Bretherton et~al.}(2005)\textit{Bretherton, Blossey, and
%  Khairoutdinov}}]{Bretherton_etal_2005}
%Bretherton, C.~S., P.~N. Blossey, and M.~Khairoutdinov (2005), An
%  energy-balance analysis of deep convective self-aggregation above uniform
%  sst, \textit{J. Atmos. Sci.}, \textit{62}, 4273--4292.
%
%%\bibitem[{\textit{Jeevanjee and Romps}(2013)}]{Jeevanjee_Romps_2013}
%%Jeevanjee, N., and D.~M. Romps (2013), Convective self-aggregation, cold pools,
%%  and domain size, \textit{Geophys.\ Res.\ Lett.}, \textit{40}, 994--99,
%%  \doi{10.1002/grl.50204}.
%  
%\end{thebibliography}

>>>>

%\textbf{Key Points: choose three}
\begin{keypoints}
%  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
 % precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
%  maximum.}
  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
  maximum away from the SST maximum.}
  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
  changes in the low-level clouds and boundary layer structure.}
  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
  region that is 30\% higher than for the coarser cases with parameterized convection.}
  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
\end{keypoints}

@@

% What are climate modelers doing to reduce uncertainties about cloud processes?
%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
%idealized equatorial tropical Pacific.

In the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective 
storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
connected by a large-scale circulation.  
We analyze this circulation with high-resolution 
and coarse resolution simulations and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the Earth's sensitivity to 
changes in greenhouse gas concentrations.

A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
resolution (25km, 100km) configured 
as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.

@@

  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
  extensively studies (review paper?).  The circulation first 
  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
  subtropics, stratocumulus clouds.  This circulation has come to be 
  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
  observations (Walker, Bjerknes), theory (Geisler, 1981), 
  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
  modeling studies have compared theoretical models with cloud
  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  

@@

Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
cumulus, and cumulus congestus clouds all interact with each other.  The Hadley circulation connects the tropical 
pacific with subtropics and has been extensively studies (review paper?).  The circulation first 
  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep 
  convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
  subtropics, stratocumulus clouds.  This circulation has come to be 
  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 
  2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations (Walker, Bjerknes), theory 
  (Geisler, 1981), or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
  Kuang, 2012)).  Some of these modeling studies have compared theoretical models with cloud
  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker 
  Circulation with simulations from a GCM used on a doubly periodic domain.

We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
show both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
we test the impact of convective parameterization, 
longwave radiation interactions with clouds, domain size, 
and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.

The results of our experiments are organized as follows.  Details of the model and the particular experiments used are described
in the next section.  The longwave cloud radiative effect is an important element for all of the experiments and will be 
discussed in all of the sections.   
Section three describes the tendency of experiments with parameterized convection to settle into states which 
do not mirror the symmetry of the prescribed sea surface temperature.   
Then, section four shows how the distribution of precipitation changes as a function of domain size.  
Section five will describe and contrast the Walker circulation in a GCM-like and a CRM-like configuration. 
Conclusions from this study will then be summarized.

@@

\begin{table}
\begin{center}
\caption{Specifications of the simulations used most heavily in this study.  In the Convection
column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.
All of the experiments listed here were also run with the longwave cloud radiative effect turned off.
These will be referred to as P100L LWCRE off, etc.  }
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
    \\
 Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection     \\ \hline
  P100L &  100          &   800 $\times$ 16000    &  60              & prm                   \\ 
    \\
  P100 &  100                & 800 $\times$ 4000     & 60            & prm                     \\  
    \\
  P25L &  25             & 200 $\times$ 16000      & 60             & prm                     \\  
    \\
  P25  &  25             & 200 $\times$ 4000      & 60             & prm                   \\  
    \\
 E25  &   25          & 200 $\times$ 4000      & 60             & expl                \\  
    \\
 E2   &   2          & 100 $\times$ 4000      & 6             & expl                   \\ 
    \\
 E1   &   1          & 10 $\times$ 4000      & 6             & expl                 \\  \hline

@@

%"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
%double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
%was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
%vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
%Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
%turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
%greater are being dominated by this second factor.

@@

When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are 
two of the most fundamental choices that must be made.   One the goals of this study was to explore the results of 
changing grid-spacing over a wide range of values.  To simplify the analysis we have in most cases chosen to keep the 
long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
\cite{Bretherton2005, Bretherton2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
have documented sensitivities of the equilibrated state to domain size for similar experiments
of radiative convective equilibrium.   
The analysis of the previous, and of the next sections focus on results from 
experiments using a domain with a long domain length of $4,000 \, \rm{km}$.  However when comparing those results
to experiments with a long domain length of $16,000 \, \rm{km}$, we find interesting 
sensitivities to the domain size that are described in this section.

The evolution in time of the precipitation field clearly illustrates how much the spatial distribution can vary as a 
function of domain size, parameterization of convection, and the effect of the longwave radiation due to clouds. 
Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovmoller plots of precipitation after 
averaging along the short horizontal dimension.  The four panels show simulations with a grid-
spacing of $25\, \rm{km}$ on a domain with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ 
(middle right), and 
simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
$16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LW CRE off.

At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
strengthen an overturning circulation and
narrow the region of deep convection (see Popp and Silvers, 2017, Harrop and Hartmann, Dixit et al. 2019.  etc.).
The structure of the precipitation changes more as a function of domain size than it does as a function of resolution. 
On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation 
meandering within 500 km of the SST maximum at the center of the domain,  
the experiments without the LW CRE basically have no region with consistently strong precipitation.  Instead, 
smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously noted, 
these GCM-like simulations equilibrate after approximately 50 days.  However, there is also a dramatic change in 
the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
precipitation does not significantly change in these cases, only the spatial structure.

An additional change that results from increasing the domain width is an upward shift of the cloud fields.  This is 
shown with the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low level maximum of 
condensate is shifted from near 900 hPa in the small domain (thin lines) to between 700-800 hPa in 
the large domain (thick lines).  There is also a vertical shift in the upper level ice condensate, but it is less
pronounced.

% new Hovmoller diagram
\begin{figure}
  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
  \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
  25km and 100km.  From left, large domain 100km, (P100L); 
  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
  For each resolution, the only difference between the two experiments shown is a domain length of 
  16,000 km or 4,000 km.}
  \label{fig:domdep}
\end{figure}

@@

The domain mean total precipitation is constrained by the radiative cooling of the atmosphere.  
However, in models with the convection parameterized, the 
total precipitation is composed of precipitation from the convection scheme and the large-scale cloud scheme. 
The relative contribution of each component is not well constrained and \citeA{Held2007} have shown 
that the fraction of the precipitation that is due to the large-scale cloud scheme is closely linked 
to low cloud cover and total condensate.  
The distribution of convective and large-scale precipitation indicates how the condensational heating
in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
Precipitation from each of these two components is
shown in Figure \ref{fig:conv_vs_ls} as a function of both resolution and domain size.  
In the regions of large-scale ascent, most of the 
precipitation derives from the large-scale cloud scheme.  
Following the terminology of \citeA{Held2007} we could say that most of the precipitation is 
coming from `gridpoint storms' in which the upper level moisture is being supplied not 
by the convective parameterization but from the boundary layer as a result of large-scale upwelling.
We also see that the LW CRE (thick lines) dramatically increases
the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective 
precipitation 
but does act to spatially concentrate it.  With the exception 
of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in P25L case
and an almost complete elimination of the large-scale precipitation in the P100L case.    
The fraction of precipitation that is due to the large-scale cloud scheme was linked to the low level cloud radiative
effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction.  
We also demonstrate that is through the longwave cloud radiative effect that this connection is enabled.

@@

Smaller domains were found to have a more focused ascent region and larger precipitation rates in B06.
They also found less low-level clouds over the colder SSTs in the small domains (1,024 km wide), relative 
to a control domain with a width of 4,096 km.   In contrast, here larger domains have larger precipitation rates (Table 2).  
We find fewer low-clouds on the large domain experiments (P25L, P100L), but a mid-level cloud 
maximum (Figure \ref{fig:TotCond_P25P100}).   There are notable differences in the domain mean condensate between 
the default and large domains.  Overall the large domains show an upward shift of condensate and have 
a much stronger upper level response to the LWCRE being turned off.
For the LWCRE off cases, in agreement with B06 we find a more 
focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the relative ascent region 
changes little between P25 
and P25L but for P100 and P100L the ascent region is much more focused on the large domain.

@@

We were struck by three particular changes due strictly do a 4-fold increase in domain width.  A dramatic widening of the precipitation distribution when the LW CRE is off, a shifting of low level clouds upward by more than 100 hPa, and 
a strong dependence of the quantity of precipitation produced by the large-scale scheme on the LW CRE.

@@

%References: 
%
%Bretherton et al. 2006
%Jeevanjee et al. 2018
%Kuang and Wofsy
%Muller and Held, 2012
%Popp and Silvers, 2017
%Patrizio and Randall, 2019
%Randall et al., 1989
%Silvers et al. 2016
%Slingo and Slingo, 1988
%Stevens et al. 2012
%Zhao et al. 2018a
%Zhao et al. 2018b

@@
